---
title       : Shiny Asssignment
subtitle    : Displaying Communes in Switzerland
author      : Christian Ruiz-Palmero
job         : PhD
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This application shows the communes in Switzerland. It consist of three crucial elements.

1. A plot that displays the communes by distinct colors depending on the cantons that they are in.
2. A slider that lets the user select a range of cantons that is to be displayed in the plot.
3. And a table that displays in text the cantonsthat were selected and plotted.

--- .class #id 

## Element 1: Slider

The following code shows the simple slider. Below you can see that the default value is a vector of 1 and 29. In other words, all the cantons are selected here.

```{r, eval=FALSE}
sliderInput("cantslider",
                   "Select the Cantons:",
                   min = 1,
                   max = 29,
                   value = c(1,29))
    ),

```



--- .class #id 
## Element 2: Plot
In principle the plot is in the form of
```{r, eval=FALSE}
plot(map_data$longitude,
      map_data$latitude,
      col=map_data$canton,
         xlab="",ylab="",pch=19)
```
However, for every variable the following conditional statement is taken, where input$cantslider[1] and input$cantslider[2] represent the two values of the slider:
```{r, eval=FALSE}
map_data$id_canton >= input$cantslider[1] & map_data$id_canton <= input$cantslider[2]
```

--- .class #id 
## Element 3: Table
Lastly, a table is rendered where the names of the cantons are displayed as text. 

```{r, eval=FALSE}
  output$range <- renderTable({ 
  },include.colnames=FALSE)
```
 The main element in this renderTable is a matrix. The matrix is created as follows and consists of two elements. The first one is a vector of the cantons that are selected:
 ```{r, eval=FALSE}
        matrix(
            c(as.character(
                  unique(
                        map_data$canton)
                        [input$cantslider[1]:input$cantslider[2]]),
```
The second part than fills the matrix with empty values as else the matrix would be filled with the first elements again.
```{r, eval=FALSE}
              rep("",8-length(input$cantslider[1]:input$cantslider[2])%%8))
```

